New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-07-08 paper/paper.Rmd
figure refences, and fig 3 was not needed

```{r othermethod, out.width="100%", width=12, height=4, fig.cap="Manual controls with algorithm 2. The precise location of the axis is maintained."}
source("../code/plot_basis.R")
source("../code/linear_alg.R")

@@

To illustrate the usefulness of the manual tour we use the 4D penguins data [@penguins]. We will show how classification boundaries can be explored and better understood using a manual tour, on projections and slices through 4D space. Figure \ref(fig:penguins-scatmat) shows a scatterplot matrix of this data. There are four variables (`bl = bill_length_mm, bd = bill_depth_mm, fl = flipper_length_mm, bm = body_mass_g`) measuring the size of the penguins from three species (Adelie, Chinstrap and Gentoo). The scatterplot matrix shows that the three species appear to be likely separable, and that at least the Gentoo can be distinguished from the other two species when `bd` is paired with `fl` or `bm`. The steps for exploring boundaries are as follows:

>>>>

```{r othermethod, eval=FALSE, out.width="100%", width=12, height=4, fig.cap="Manual controls with algorithm 2. The precise location of the axis is maintained."}
source("../code/plot_basis.R")
source("../code/linear_alg.R")

@@

To illustrate the usefulness of the manual tour we use the 4D penguins data [@penguins]. We will show how classification boundaries can be explored and better understood using a manual tour, on projections and slices through 4D space. Figure \ref{fig:penguins-scatmat} shows a scatterplot matrix of this data. There are four variables (`bl = bill_length_mm, bd = bill_depth_mm, fl = flipper_length_mm, bm = body_mass_g`) measuring the size of the penguins from three species (Adelie, Chinstrap and Gentoo). The scatterplot matrix shows that the three species appear to be likely separable, and that at least the Gentoo can be distinguished from the other two species when `bd` is paired with `fl` or `bm`. The steps for exploring boundaries are as follows:

### 2022-07-08 paper/paper.tex
figure refences, and fig 3 was not needed

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figure-latex/othermethod-1} \caption{Manual controls with algorithm 2. The precise location of the axis is maintained.}\label{fig:othermethod}
\end{figure}

@@

To illustrate the usefulness of the manual tour we use the 4D penguins
data \citep{penguins}. We will show how classification boundaries can be
explored and better understood using a manual tour, on projections and
slices through 4D space. Figure \ref(fig:penguins-scatmat) shows a
scatterplot matrix of this data. There are four variables
(\texttt{bl\ =\ bill\_length\_mm,\ bd\ =\ bill\_depth\_mm,\ fl\ =\ flipper\_length\_mm,\ bm\ =\ body\_mass\_g})
measuring the size of the penguins from three species (Adelie, Chinstrap
and Gentoo). The scatterplot matrix shows that the three species appear
to be likely separable, and that at least the Gentoo can be
distinguished from the other two species when \texttt{bd} is paired with
\texttt{fl} or \texttt{bm}. The steps for exploring boundaries are as
follows:

>>>>

@@

To illustrate the usefulness of the manual tour we use the 4D penguins
data \citep{penguins}. We will show how classification boundaries can be
explored and better understood using a manual tour, on projections and
slices through 4D space. Figure \ref{fig:penguins-scatmat} shows a
scatterplot matrix of this data. There are four variables
(\texttt{bl\ =\ bill\_length\_mm,\ bd\ =\ bill\_depth\_mm,\ fl\ =\ flipper\_length\_mm,\ bm\ =\ body\_mass\_g})
measuring the size of the penguins from three species (Adelie, Chinstrap
and Gentoo). The scatterplot matrix shows that the three species appear
to be likely separable, and that at least the Gentoo can be
distinguished from the other two species when \texttt{bd} is paired with
\texttt{fl} or \texttt{bm}. The steps for exploring boundaries are as
follows:
